### 2016-10-25 sec-related-work.tex
Add Bayesian Knowledge Tracing related work; reorganize that section.

Our model is based heavily upon the prior art of Hidden Markov
Models~\cite{Rabiner:1990:RSR} for sequence labeling tasks. These types of
models are widely applicable and have been used for tasks such as speech
recognition~\cite{Huang:1990:HMM} and part-of-speech
tagging~\cite{Jurafsky:2009:SLP}. We employ maximum likelihood estimation
for estimating our model parameters using the EM algorithm
framework~\cite{Dempster:1977:JRSS} by modifying the Baum-Welch algorithm
for traditional HMMs~\cite{Rabiner:1990:RSR}.

@@

\citet{Shih:2010:EDM} investigate the use of HMM-based clustering
techniques for automatic discovery of student learning strategies when
solving a particular problem. This is similar to our approach in that the
description of behavior profiles is a Markov-model, but differs in focus:
we investigate macro-level MOOC behavior here as opposed to looking at
individual problem solving behavior. \citet{Ypma:2002:Springer} use
mixtures of HMMs to categorize web pages and cluster users by investigating
web log data, which is quite similar to the clickstream log data we obtain
from MOOCs.

>>>>

\subsection{Hidden Markov Models}
Our model is based heavily upon the prior art of Hidden Markov
Models~\cite{Rabiner:1990:RSR} for sequence labeling tasks. These types of
models are widely applicable and have been used for tasks such as speech
recognition~\cite{Huang:1990:HMM} and part-of-speech
tagging~\cite{Jurafsky:2009:SLP}. We employ maximum likelihood estimation
for estimating our model parameters using the EM algorithm
framework~\cite{Dempster:1977:JRSS} by modifying the Baum-Welch algorithm
for traditional HMMs~\cite{Rabiner:1990:RSR}.

\citet{Shih:2010:EDM} investigate the use of HMM-based clustering
techniques for automatic discovery of student learning strategies when
solving a particular problem. This is similar to our approach in that the
description of behavior profiles is a Markov-model, but differs in focus:
we investigate macro-level MOOC behavior here as opposed to looking at
individual problem solving behavior.

\subsection{Bayesian Knowledge Tracing}
Bayesian Knowledge Tracing~\cite{Corbett:1994:UMUAI} in its basic form uses
a hidden Markov model to model the probability that a learner knows a
certain skill at a given time. Modifications to this algorithm include
contextual estimation of the ``slip'' and ``guess'' probabilities of the
model~\cite{Baker:2008:ITS} and most recently a re-framing as a neural
network problem~\cite{Piech:2015:NIPS}.

\subsection{Mixtures of Markov Models}
\citet{Ypma:2002:Springer} use mixtures of HMMs to categorize web pages and
cluster users by investigating web log data, which is quite similar to the
clickstream log data we obtain from MOOCs.

@@
